In the framework of indoor mobile robotics, \emph{place recognition}
is a complex and challenging task. In domotics, for instance, a mobile
robot may be required to navigate through the rooms of a flat; it is
then crucial that self-localisation be enforced precisely,
notwithstanding the changing conditions of illumination, objects being
shifted around and/or people and other obstacles momentarily changing
the appearance of the scene.

In such a complex and multivariated problem involving robotic vision,
continuous learning seems the main way out, thanks to the possibility of
adapting to changes in a smart and flexible way. Nevertheless,
standard machine learning approaches usually suffer when confronted
with massive amounts of data and when asked to work on-line, that is,
when the flow of data is continuous and not guaranteed to ever
cease. On-line learning requires a high training speed, all the more
in place recognition, where a continuous flow of data comes from one
or more cameras.

In this paper we 
follow the SVM-based approach proposed by Pronobis et al \cite{pronobis:iros06},
and we
propose a new approach to the problem that we call
Online Independent Support Vector Machines. This technique exploits
linear independence in the image feature space to incrementally keep
the size of the learning machine remarkably small while retaining the
accuracy of a standard machine. Since the training and testing times
crucially depend on the size of the machine, this solves the above
stated problem. This claim is supported by  experimental results
achieved on the IDOL2 database, 
a recently introduced collection that
contains $24$ image sequences 
of a five rooms environment, acquired using a perspective camera across a time span of several months.
