% On the use of motor invariants for speech recognition
% Castellini, Metta, Fadiga, Tavella (?)
% submitted to PNAS

\documentclass{pnastwo}

% remove for submission
\usepackage[dvips]{graphicx}

\usepackage{amssymb,amsfonts,amsmath}

\contributor{Submitted to Proceedings of the National Academy of Sciences of the United States of America}
\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
\copyrightyear{2008}
\issuedate{Issue Date}
\volume{Volume}
\issuenumber{Issue Number}

\begin{document}

\title{On the use of motor invariants in speech classification}

\author{
Claudio Castellini\affil{1}{LIRA-Lab, University of Genova, Italy},
Giorgio Metta\affil{2}{Italian Institute of Technology, Genova, Italy} \and
Luciano Fadiga\affil{3}{DSBTA, University of Ferrara, Italy}
%Giorgio Metta\affil{2}{Italian Institute of Technology, Genova, Italy},
%Luciano Fadiga\affil{3}{DSBTA, University of Ferrara, Italy} \and
%Michele Tavella\affil{4}{EPFL, Lausanne, Switzerland}
}

\contributor{Submitted to Proceedings of the National Academy of Sciences
of the United States of America}

\maketitle

\begin{article}

\begin{abstract}

  The use of phonetic motor invariants (recurring kinematic patterns)
  to improve speech classification is here investigated. The
  idea is inspired by the Motor Theory of Speech perception, as well as
  from recent findings about the interplay between speech
  perceptual and motor areas in the brain. Using a multi-subject database
  of synchronised speech and lips/tongue trajectories, we first detect
  motor invariants associated with bilabial and dental consonants.
  We then show that automated classification of these
  consonants is radically improved by adding the motor invariants to
  standard audio features. Lastly, we show that the very same invariants can be
  automatically reconstructed from the audio features to such a degree of
  precision that they still uniformly improve the classification; the
  reconstruction, too, is based upon the human data.
  This result encourages the systematic use of motor invariants to build
  better speech recognition systems. Moreover, some of the issues found in
  the analysis seem to shed light on the mechanisms of human speech perception
  --- mainly, to support the claims of the motor theory of speech.
  
\end{abstract}

\keywords{motor theory of speech | machine learning | speech recognition}

\input{10.intro}
\input{20.dataset}
\input{30.segm}
\input{40.class}
\input{50.rec}
\input{60.disc}
\input{70.concl}

\begin{acknowledgments}
  This work is supported by the EU-funded project Contact (NEST 5010).
\end{acknowledgments}

%\begin{thebibliography}{}
%
%\end{thebibliography}

\end{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Adding Figure and Table References
%% Be sure to add figures and tables after \end{article}
%% and before \end{document}

%% For figures, put the caption below the illustration.
%%
%% \begin{figure}
%% \caption{Almost Sharp Front}\label{afoto}
%% \end{figure}

%% For Tables, put caption above table
%%
%% Table caption should start with a capital letter, continue with lower case
%% and not have a period at the end
%% Using @{\vrule height ?? depth ?? width0pt} in the tabular preamble will
%% keep that much space between every line in the table.

%% \begin{table}
%% \caption{Repeat length of longer allele by age of onset class}
%% \begin{tabular}{@{\vrule height 10.5pt depth4pt  width0pt}lrcccc}
%% table text
%% \end{tabular}
%% \end{table}

%% For two column figures and tables, use the following:

%% \begin{figure*}
%% \caption{Almost Sharp Front}\label{afoto}
%% \end{figure*}

%% \begin{table*}
%% \caption{Repeat length of longer allele by age of onset class}
%% \begin{tabular}{ccc}
%% table text
%% \end{tabular}
%% \end{table*}

\end{document}
