
\section{Acknowledgments}

YARP and ICub make heavy use of software released under free and open
licenses -- thank you world.
%
The authors would like to gratefully acknowledge contributions to YARP
from Alessandro Scalzo, Francesco Nori, Radu Bogdan Rusu, 
Alexis Maldonado, Eric Mislivec, Christopher
Prince, Charles C. Kemp, Julio Gomes, Alexandre
Bernardino, Carlos Beltran, Jonas Ruesch, Assif Mirza, Hatice
Kose-Bagci, Mike P. Blow, Lars Olsson,
Jose Gaspar, Claudio Castellini, Michael Bucko, Nelson
Gon\c calves, Marco Barbosa, Tomassino Ferrauto, Boris Duran, Mattia
Castelnovi, and Giacomo Spigler 
 (if we missed anyone, plese let us
know).  
%
The ``yarpimage'' driver mentioned in Section~\ref{sect:interop}
was written by Radu Bogdan Rusu.

We are happy to be just one set of contributors to the ICub platform
amongst the larger team of the RobotCub Partners and the RobotCub
Consortium.
%
ICub software contributers include (with some overlap with YARP):
Alessandro Scalzo, Alexandre Bernardino, Alexis Maldonado, Basilio
Noris, David Vernon, Eric Sauser, Micha Hersch, Fabio Berton, 
Jonas Hornstein, Jonas Ruesch, Lijin Aryananda, 
Ludovic Righetti, Manuel Lopes, Julio Gomes, Plinio
Moreno, Vadim Tikhanoff, and 
the authors (if you are not listed, please check that
you have correctly placed a copyright and copy-policy statement in
your source code).
%
%
The simulators shown in Figure~\ref{fig:simulators} were developed 
by Ludovic Righetti (Webots-based simulator) and
Vadim Tikhanoff (ODE-based simulator).
%
Our thanks to the reviewers for their constructive feedback, which
made this a better paper.
%
The authors were supported by European Union
grant RobotCub (IST-2004-004370).




