
\section{Conclusions}

In recent years we have seen the beginning of many new and 
ambitious robotic projects 
\cite{02-c59-Hirai-1998,02-c59-Kaneko-2004,adams00humanoid,02-c59-Sakagami-2002}. 
%
However research to provide intelligence 
to these complicated robots is advancing at a snail's pace.
%
Accumulating knowledge in the form of working demonstrable systems is 
plagued by the difficulty of forming teams, on agreeing on standards, and 
in general by the lack of a critical mass in any existing laboratory no 
matter the size or funding. 

%% ok this looks too much like another introduction, might need to 
%% be shortened but perhaps could help to make a concluding point
%% if linked to the story of the PC and the need for standards...
%%
The problem of artificial intelligence is a deep one, and since
it began to be investigated, each
generation of researchers has grossly underestimated the problems.
%
For example, the Summer Vision Project of 1966 at the
MIT AI Lab planned to implement figure/ground separation
and object recognition on a set of objects such as balls and
cylinders in the month of July, and then extend that to cigarette
packs, batteries, tools and cups in August \cite{papert66summer}.
%
As it turns out, if they had written decades rather than months, it
would still have been over-ambitious.
%
% \ref{} and the year 2006 
%celebrated the $50^{th}$ anniversary of the workshop at Dartmouth College
%which is unanimously considered the birth of artificial intelligence at 
%least in some modern sense \ref{}. %Turing had previously considered the problem%
%A generation of researchers did not manage to make the progress that was
%certainly hoped for. 
%
Significant progress can certainly be made either 
because of a breakthrough in our understanding of the problems or through 
a slower accumulation of knowledge. Or it can be due to a combination of 
these two elements. 
%
%The recent paradigmatic shift toward 
%
We, like many others, are drawn to robotics as a way to confront the 
``real'' problems of intelligence head on.
This has the advantage of exposing unforeseen opportunities that
embodiment brings with it \cite{YARB}, but the downside that
it requires a lot of time spent building hardware.
%
It would be beneficial to build a community
that can accumulate knowledge and make effective progress,
and to expand the niche of
humanoid robotics and artificial intelligence to the point where it 
is healthy and self-sustaining.

In this respect, the parallel with the commercial PC is easily made. 
The success of the PC was determined, among other factors, by the definition 
of hardware standards that everybody could understand, copy, and reimplement. 
From time to time new standards were required (e.g. the ISA bus slowly left
space to PCI slots) but the system flourished. Under the hood, the PC is a 
few orders of magnitude faster and of larger
storage capacity. On the software side, the benefit of a common architecture
allowed the creation of operating systems and application software consisting of 
several millions of lines of code. Without a standard hardware things
might have been more difficult.
%
A PC of today is the modern 
version of the Ship of Theseus\footnote{The Ship of 
Theseus -- the mast gets replaced,
the planks get replaced, over time everything may get replaced,
but it is still in some important sense the same ship (``paradox
of identity'')}, everything changed but the PC is still considered
a PC. 
%

Is robotics really facing the same challenges as the computer industry
three decades ago~\cite{gates2007robot}? 
%
It is clearly difficult to foresee the future of humanoid robotics. However
a few dedicated software platforms are appearing as either 
commercial~\cite{microsoft}
or academic~\cite{vaughan2006reusable} products (see also 
\cite{kramer2007development} for a survey). It is
easier %though% 
to imagine a scenario where common standards both in 
software and hardware will find the fertile soil to flourish when 
isolated breakthroughs will happen.
%
%%% this paper is now cited elsewhere
%A survey of robot development environments
%\cite{kramer2007development} (p.s. rules YARP out, claim it has
%no coherent program, think they were seeing YARP1).
%
% \cite{gerkey03player} % redundant to newer paper
%
% Not sure why this is here \cite{natale05developmental}

The problem of dealing with diverse hardware and software 
in robotics is a complicated one -- see \cite{nesnas2006claraty} 
for a good description of the many and various problems.
%
The key insight from the Free Software community is the value
a common social contract, granting mutually beneficial rights
that greatly reduce both the direct and organizational cost
of software integration.  Regardless of the technical
measures we pursue, adopting such a social contract
in at least a part of the humanoid robotics community would
be a key advance.
%
We believe that this will occur naturally ``bottom-up''
through pseudo-evolutionary forces: models of software 
development that are long-lived and fertile will survive,
other forms will die off.
%
The rate at which this will occur is hard to say,
and could be influenced by education.
%
For example, a common fear is that such approaches are incompatible
with commercial exploitation; in fact they are not, as has been
learned in many other fields including embedded
devices~\cite{henkel2006selective}.  They do change the rules of the
game though, which is disruptive.
%
We should welcome that disruption.

% so reluctance to explore novel
%business models is to be expected.

%%% this paper is now cited elsewhere
%%Vaughan \cite{vaughan2006reusable} - this is a good player/stage
%%paper.


%Our previous comments on YARP1 \cite{metta2006yarp} which
%describe its history and some usage information.


%Missing infrastructure.
%Need a lot of software.
%Ideally (for researchers starting out) should be commoditized.
%Free software is doing that.
%
%Consider the effect of the KLT tracking code; by no means
%the best in the world, but was available and still used
%today for that reason.


%comparison with PC:
%Difference: now we have the network.  Go the player route, rather than
%the single IDE.  Transform from hardware to open protocols as first
%step.  Then whole ecology of computation is available.


%The resources available to us are generally lower.  Smaller communities.
%Less software expertise.  This could chage.

%Robots aren't that special.  webcam/microphone/games...
