\section{Discussion} \label{Discussion}

With this experiment we aimed at finding out whether a strategy based on some kind of force field model of a flying object could be involved in the prediction required to intercept it, and consequently on what sort of information prediction could be based.
The experiment proposed suggests that dynamic information may play a role in prediction for interception. The trajectories subjects had to deal with were different in each trial, because of different initial ball positions and velocities, in all experimental conditions. In one of them a unique force field drove the ball during all the trials, in the other condition, instead, different fields characterized each trial. The trajectories were however always parabolic and presented therefore always the same shape. The significant difference between performances in the two conditions, then, should be related to the different dynamical characteristics (different kind of force fields) of the tasks. According to our view in the fixed field protocol subjects adjusted an internal model of the forces acting on the ball and adopted this model to score a better performance in prediction.
This kind of process is in a certain sense related to that used by subjects in the experiment described by Mussa-Ivaldi, who learned to correctly perform reaching movements immersed in a force fields modeling the force perturbing their arm and counterbalancing it. This hypothesis is then already an attempt to give an affirmative answer to the first question: subjects rely on internal models in object interception prediction.
This idea is also supported by the \textit{Transfer Effect} observed when the fixed force field is suddenly turned off, replaced by a vertical force that changes randomly its orientation at each trial. In particular subjects show no adaptation phases after the error peak and return immediately in trend with their previous performance, as they could simply switch to a model already learned.

\textcolor{red}{In particular this model appears to be refined during the first blocks of trials, in which subjects progressively tune their evaluations and succeed in predicting the trajectory as parabolic also when the ball is hidden behind the wall. When the force field generating the trajectories changes at each trial, instead, the model cannot be built and probably subjects rely on a different and less effective predictive strategy, based for instance on the interpolation of the last part of ball trajectory with a straight line.}

Furthermore it seems that the process of dynamic modeling does not depend on a particular value of the force field. In this experiment, in fact, errors made in the fixed force field case, both when it was upward and when it was downward oriented were always lower than those performed when there was no possibility to model the force, because of its variability. 

Given that the central nervous system effectively relies on dynamic cues to exploit this kind of prediction, it remains to understand how this information is collected. A further result of our experiments could give suggestions on this topic.
We observed that subjects who had to intercept balls moving in a force field similar to gravity (a vertical force  oriented downward) performed always better than those who dealt with an identical but symmetrical force (upward oriented). People were asked to intercept the target by shifting up and down a small virtual paddle by actually moving their hand up and down. They had therefore to perform an action as at the same time they were experiencing the gravitational force. We assume that what affected the results of those who intercepted balls in the ``anti-gravitational'' field was the opposition between the force felt and that seen on the screen. 
\textcolor{red}{Of course the ``pseudo - gravitational'' case could be also easier due to our everyday experience with gravity and therefore the results observed could be also explained by theories proposed in \citep{McIntyre}, \citep{Lacquaniti}, \citep{Lacquaniti_internal} and \citep{McIntyre2}. However we postulate that both these elements, and not only the latter, cause the difference in performances between ``anti-gravitational'' and ``pseudo-gravitational''  conditions.
Therefore we are currently designing a new experimental procedure to isolate the effect of the coherence between fields felt and seen in facilitating prediction.}

%In order to prove our theory we have to design a new experimental procedure which will be part of our future work.

Moreover we are postulating that performing a real action to intercept the target and thus actively involving the motor system is important to the prediction itself. In particular according to our view the motor system has a role in managing dynamic information, so that models used in interception could be different when the motor system is activated or not.
It has been proposed that we can understand better what happens by mapping other people's movements to our own, and that this is obtained through the sub-threshold activation of our muscles \citep{Wolpert_social}. Therefore we can suggest that the complete activation of our motor system could be the means by which we can obtain the contextual dynamical structure.

 
%This hypothesis seems to explain some results obtained during an experiment proposed by McIntyre and colleagues \citep{Lacquaniti}. They showed that if a subject is asked to punch a ball which appears at the end of a screen in concurrence with a virtual ball falling along the screen, he times his movements as if he predicted a gravitational acceleration, whatever the real motion is. However when the subject in the same condition must instead ''explode'' the virtual ball by pressing a button and not punching the ball, the timing is tuned to a constant velocity motion, irrespective of the real motion of the ball. According to our theory this difference can be accounted by the fact that the motor system in the second case is not involved as much as in the first. When it is activated to produce an action, it enters also the process to realize a prediction and force the system to take into account also force information, on line or previously estimated (in this particular case gravitational force.)

Our work does not aim at describing how this process is realized, but it represents the first step in the developing a unifying approach, in which prediction of inanimated objects interception is based on similar, though different, principles as prediction of human movements. 
 

%Our work does not aim at describing how this process is realized, but just at suggesting a direction of investigation.
%This model of prediction could also be seen as a an effort to propose a unifying approach, in which prediction of inanimated objects interception is based on similar, though different, principles as prediction of human movements. 

% Prediction would find actually a place among all the other skills in which perception and action are strictly linked. This skill, at least in object interception, could be actually somehow inserted in a particular ''mirror'' framework, in which action and perception become strictly linked. 

%One future development of the experiment proposed could be reproducing the same task but in force fields different from gravity, for instance with a manipolandum. It would be then possible to understand better how the motor information helps in this kind of prediction tasks.

