%
% Gaze Tracking in Semi-Autonomous Grasping
% Submitted to JEMR special issue
% Castellini
%

\documentclass{article}

\usepackage{float}
\usepackage{graphicx}
\usepackage{url}
\usepackage{amsmath}
\usepackage[psamsfonts]{amssymb}

\def\RR{\mathbb{R}}
\def\NN{\mathbb{N}}
\def\xx{\mathbf{x}}
\def\yy{\mathbf{y}}
\def\ww{\mathbf{w}}
\def\aa{\boldsymbol{\alpha}}
\def\bb{\boldsymbol{\beta}}
\def\ee{\mathbf{e}}
\def\dd{\mathbf{d}}
\def\mdd{\tilde{\dd}}
\def\b{\mathcal{B}}
\def\d{\mathcal{D}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\LARGE \bf Gaze Tracking in\\ Semi-Autonomous Grasping}

\author{Claudio Castellini}

\date{}

\begin{document}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

In critical human/robotic interactions such as, e.g., teleoperation by
a disabled master or with insufficient bandwidth, it is highly
desirable to have \emph{semi-autonomous} robotic artifacts interact
with a human being. Semi-autonomous grasping, for instance, consists
of having a smart slave able to guess the master's intentions and
initiating a grasping sequence whenever the master wants to grasp an
object in the slave's workspace.

In this paper we investigate the possibility of building such an
intelligent robotic artifact by training a machine learning system on
data gathered from several human subjects while trying to grasp
objects in a teleoperation setup. In particular, we investigate the
usefulness of gaze tracking in such a scenario. The resulting system
must be light enough to be usable on-line and flexible enough to adapt
to different masters, e.g., elderly and/or slow.

The outcome of the experiment is that such a system, based upon
Support Vector Machines, meets all the requirements, being $(a)$
highly accurate, $(b)$ compact and fast, and $(c)$ largely unaffected
by the subjects' diversity. It is also clearly shown that gaze
tracking significantly improves both the accuracy and compactness of
the obtained models, if compared with the use of the hand position
alone. The system can be trained with something like $3.5$ minutes of
human data in the worst case.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
\label{sec:intro}
\input{paper_intro.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{MATERIALS AND METHODS}
\label{sec:matmet}
\input{paper_matmet.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EXPERIMENTAL RESULTS}
\label{sec:res}
\input{paper_res.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{DISCUSSION AND CONCLUSIONS}
\label{sec:concl}
\input{paper_concl.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{ACKNOWLEDGMENTS}

The work is supported by the EU-funded project NEURObotics
(FP6-IST-001917). We thank Giulio Sandini and Giorgio Metta of the
Italian Institute of Technology and Francesco Orabona of IDIAP
Switzerland for their support.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\small
\bibliographystyle{alpha}
\bibliography{paper}
}

\end{document}
