
Is there a way to talk about development that works
for robotics and infants?  There are two approaches
that might work.  One is to focus on common ground,
and selectively model what robots and infants may
have in common.  Another approach is to develop
a general model which can be instantiated for
infants and robots.  This is not very 
ambitious, but would at least provide a common lanuage.




Let's call a value or bundle of values a ``unit''.  We aren't
too concerned with the nature of those values right now.  Let's 
just say for now that perception for our robots and infants will
be modeled as the process of producing these units.

Let's also have ``modules'' which connect to a set of units,
reading the values of some of them (input units) and setting
the value of others (output units).

In our model, we will assign meaning to units, by saying
what a unit should compute.  This is not part of the
structure that the model describes.  What a unit actually
computes can vary from what we say it should.

We will often have pairs of units, where one unit can
be interpreted as a ``confidence'' value on the other unit.

We can talk of a unit being ``active'', in that case we
assume it is a value between 0 and 1, and is above 0.5.

We are concerned with at least two kinds of processes.

{\bf Unit Support}  If u1 and u2 are units,
with u2 meaning the confidence of u1,
and m is a module that produces u1 and u2,
we will be concerned with processes that modify
m so that u2 becomes active more of the time,
while u1 preserves its meaning.  Note that 
the process itself doesn't have access to meaning.

{\bf Unit Creation} We need processes that
make units that are meaningful and useful.

The easy part - training; module connected to a set of units,
some designated input, some output, some training.  unit 
shadowing or gating.

Given a two part model (units and modules) need a way to 
create both, unless have a static module structure.  For now,
let's go with static module structure.


\subsection{Examples}

Orientation filter.

Unit support for object boundary.

Unit creation - clustering for object recognition.


\subsection{Johnson}

redraw Johnson's connectionist model.

values: yes/no/indeterminate?

\subsection{Robot}

redraw Cog.

\subsection{Scrap}

Processes can recruit action.


PAST LANGUAGE:
  e.g. bootstrap from situation where confident about P to other situations
  by discovering correlates -- sort of simple machine learning.

  construct new units - e.g. object rec clustering.


Also need maintenance.


