% Towards Adaptive Hand Prosthetics
% Castellini, Gruppioni, Davalli, Sandini
% submitted to Journal of Physiology, Paris
%
% March, 2009

\documentclass[journal]{IEEEtran}

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[psamsfonts]{amssymb}
\usepackage{url}

\def\RR{\mathbb{R}}
\def\NN{\mathbb{N}}
\def\xx{\mathbf{x}}
\def\yy{\mathbf{y}}
\def\ww{\mathbf{w}}

\begin{document}

\title{Towards Adaptive Hand Prosthetics}

\author{Claudio~Castellini, Emanuele~Gruppioni, Angelo~Davalli, Giulio~Sandini%
\thanks{Manuscript received on ... . This work was supported in part
  by the EU project NEURObotics (FP6-IST-001917).}%
\thanks{C. Castellini \emph{(corresponding author)}
  is with the LIRA-Lab, University of Genova,
  viale F. Causa, 13, 16145 Genova, Italy.
  e-mail: claudio.castellini@unige.it.}%
\thanks{E. Gruppioni and A. Davalli
  are with the INAIL Centro Protesi,
  via Rabuina, 14, 40054 Vigorso di Budrio (Bologna), Italy.
  e-mail: \{e.gruppioni,a.davalli\}@inail.it.}%
\thanks{G. Sandini
  is with the RBCS Department, Italian Institute of Technology,
  via Morego, 30, 16163 Genova, Italy.
  e-mail: giulio.sandini@iit.it.}%
\thanks{\textbf{NOTE} for the reviewers of this paper: a preliminary,
  limited analysis of some of the data presented in this paper has
  been submitted to a rehabilitation medicine journal as a ``short
  report'', and is currently under review.}%
}

\maketitle

\begin{abstract}
  \input{00.abstract}
\end{abstract}

%\begin{IEEEkeywords}
%  rehabilitation robotics, learning and adaptive systems, AI reasoning
%  methods, hand prosthetics.
%\end{IEEEkeywords}
%
\IEEEpeerreviewmaketitle

\section{Introduction}
\label{sec:intro}
\input{10.intro}

\section{Materials and Methods}
\label{sec:m&ms}
\input{20.mms}

\section{Data Pre-processing and Preliminary Analysis}
\label{sec:pre}
\input{30.pre}

\section{Experimental Results}
\label{sec:exp}
\input{40.exp}

%\section{A Realistic Implementation}
%\label{sec:impl}
%\input{50.impl}

\section{Discussion and Conclusions}
\label{sec:disc}
\input{60.disc}

\section*{Acknowledgments}

The authors would like to thank Mr. Cesare Stagni of INAIL Centro
Protesi for kindly helping us finding the patients who have joined the
experiment. We also thank Benoni B. Edin of Ume\aa\ University,
Sweden, for a helpful comment on the paper.

\bibliographystyle{IEEEtran}
\bibliography{paper,../../claudio}

%% \begin{IEEEbiography}{Claudio Castellini}
%% Biography text here
%% \end{IEEEbiography}

%% \begin{IEEEbiography}{Emanuele Gruppioni}
%% Biography text here
%% \end{IEEEbiography}

%% \begin{IEEEbiography}{Angelo Davalli}
%% Biography text here
%% \end{IEEEbiography}

%% \begin{IEEEbiography}{Giulio Sandini}
%% Biography text here
%% \end{IEEEbiography}

\end{document}
