
\iflong
\begin{abstract}
\else
\begin{Abstract}
\fi

Vision and manipulation are inextricably intertwined in the primate
brain.  Tantalizing results from neuroscience are illuminating the
mixed motor and sensory representations used by the brain during
reaching, grasping, and object recognition.  We now know a great deal
about {\it what} happens in the brain during these activities, but not
necessarily {\it why}.  Is the integration we see functionally
important, or just a reflection of evolution's disdain for sharp
modularity?  We wish to instantiate these results in robotic form to
probe their technical advantages and to find any lacunae that exist in
the models.  We believe it would be missing the point to investigate
this on a platform where dextrous manipulation and sophisticated
machine vision are already implemented in their mature form, and 
instead follow a developmental approach from simpler primitives.

We begin with a precursor to manipulation, simple poking and prodding,
and show how it facilitates object segmentation, a long-standing
problem in machine vision.  The robot can familiarize itself with the
objects in its environment by acting upon them.  It can then recognize
other actors (such as humans) in the environment through their effect
on the objects it has learned about.  We argue that following causal
chains of events out from the robot's body into the environment allows
for a very natural developmental progression of visual competence, and
relate this idea to results in neuroscience.


\ifverbose
This is already enough for the robot to
familiarize itself with a set of objects and the actions it can apply
to them.

If there are any
technical advantages to the integration we see, we are unlikely to
find them this way.  Instead we begin with a simple precursor to
manipulation, namely poking and prodding, and already realize
significant advantages in visual processing, and make enough progress
to develop a system that is functionally analogous to models coming
out of neuroscience.

We show how operational concepts can actually lead to well grounded
objects.
\fi


\ifverbose
For the purposes of manipulation, we would like to know what parts of
the environment are physically coherent ensembles -- that is, which
parts will move together, and which are more or less independent.  It
takes a great deal of experience before this judgement can be made
from purely visual information.  This paper develops active strategies
for acquiring that experience through experimental manipulation, using
tight correlations between arm motion and optic flow to detect both
the arm itself and the boundaries of objects with which it comes into
contact.  We argue that following causal chains of events out from
the robot's body into the environment allows for a very natural
developmental progression of visual competence, and relate this idea 
to results in neuroscience.
\fi

\ifverbose
For the purpose of understanding development we would like to present
causality as a possible principle to frame a number of neural science
results coherently. We will show how this can lead also to an
implementation in an artificial system following the epigenetic
approach. To this purpose we will show different levels of causal
linkages, or instances of the general principle, which allow tasks of
increasing complexity to be implemented.  Action and the physical
interaction of the robot with the environment play a fundamental role.
In an ecological perspective, the role of this physical interaction
for developing categorization and object undestanding is emphasized.
\fi

%%{\bf \em
%%\iflong
%%(long version)
%%\else
%%(short version)
%%\fi
%%}

\iflong
\end{abstract}
\else
\end{Abstract}
\fi
