As far as regression is concerned, the results presented above
are, to the best of our knowledge, totally novel. Given the good
performance obtained by our models, we claim that the relationship
between the EMG signal and the force has been captured by the
models, under variable conditions of muscle fatigue (within one
session) and electrode displacement (within sessions belonging to
different groups).

One remarkable point, to be further investigated, is the
\emph{correct} sampling of the EMG signal. The signal presents, as
already said, a wide variance due to a number of factors. Our work
shows clearly that, if the relevant data only is gathered, a
remarkable accuracy, both in classification and regression, can be
achieved. So far, this has been done using $(a)$ the
uniformisation procedure to \emph{reduce} the training sets, that
is, to eliminate form the training sets irrelevant data; and $(b)$
a careful a-posteriori selection of the models which had performed
best on a thorough cross-sessions analysis.

Both procedures, actually, can be seen as the need to sample the
relevant portion of the input space in a uniform way. One can think of
an online version of the uniformisation procedure, in which new
samples deemed irrelevant (according to a suitable inter-sample
distance measure, such as the Mahalanobis distance) are rejected and
never used for training. The same procedure would, when presented with
samples sufficiently distant from the current training set, decide to
actually use them. This could possibly lead to an incrementally
growing training set, which would eventually reach a plateau, when all
relevant portions of the input space have been explored by the user.

The current setup and analysis can be improved in a number of
ways, inclding a better way of gathering the force at the finger
joints, subsampling, pre- and post-filtering, and sampling in
different positions of the arm (not only the forearm), and/or
while the arm is moving.
