Our experimental results, performed on a large data set of about
$153,000$ samples, clearly show that Online Uniformisation can be used
to obtain dramatically smaller training sets with no
\emph{qualitative} loss of information; in other words, as more of the
input space is sampled, OU keeps the training set up-to-date and
small. OU sets will result in small (and therefore, fast) and accurate
models of the sought-for EMG-to-hand map. Remarkably, OU works fine
for both grasp classification and force regression, and with all three
different machine learning approaches tested. Moreover, it is
extremely simple, being nothing more than an online check of Euclidean
distance in the input space. This check is done so far by considering
the new sample's distance from all samples in the current training
set, and therefore could become unfeasibly heavy as the set grows; but
the same check can be clearly done in constant time using an
algorithmic optimisation, such a hash table.

Moreover, OU will produce models which perform \emph{uniformly} well,
enabling a patient to drive the prosthesis with a good accuracy in
\emph{all} situations that might arise, no matter how frequently they
appear during the training phase.

The choice of the minimum inter-sample distance $d$ is obviously
crucial and depends on the required accuracy in classification and/or
regression; but as we have seen, as $d$ is increased, the machine's
performance degrades only linearly, whereas the training sets become
polynomially smaller. Therefore, at the price of having a slightly
worse performance, dramatically smaller training sets can be used.

To sum up, in this paper we have presented a machine learning
approach to joint classification of grasping and regression on the
applied force, using forearm surface electromyography. The approach is
totally non-invasive, easy to set up and use and it can be applied
from scratch with no previous knowledge of the problem. The Online
Uniformisation procedure can be used to incrementally build a training
set which will result in small and accurate models of the problem.

Our experiments, carried out using a Support Vector Machine with
Gaussian kernel, a Neural Network with sigmoidal activation function
and Locally Weighted Projection Regression, indicate that the approach
achieves, using a training set of about $1800$ samples on a total of
$153,000$ (for $d=0.21$), an average accuracy of around $90\%$ in
classification of grasp types and a normalised root MSE of $7.89\%$ in
prediction of the force applied during the grasp. Of the tested
approaches, SVM is marginally better than the others, especially when
larger training sets are used. The OU procedure is able to find as
small a training set as $77.4$ samples on average (out of $153,000$),
which will still result in a SVM having a remarkable NRMSE of
$12.12\%$.

\subsection*{Future work}

We believe this is the first step toward the real application of
machine learning to an EMG-driven adaptive, dexterous AHP. Let us
consider the problems outlined in section
\ref{subsubsec:electrodes}: in this paper we have solved problems
$3$ and $4$. Now, since OU lets us obtain good accuracy with extremely
small training sets, it is not too far-fetched to say that the
solution of problem $2$ is at hand --- in principle, the changing arm
posture can be taken into account simply by sampling more of the input
space. As far as problem $1$ is concerned, inter-subject usability is
really of lesser interest, since one patient only is supposed to ever
wear a prosthesis; on the other hand, multi-subject analysis has to be
carried out eventually, since it must be possible to obtain good
results on \emph{any} subject the method is applied to. We see no
reason, however, why this should not be the case, at least as far as
able-bodied subjects are concerned.

The ultimate problem is of coruse that of training the system upon
amputees. First of all, the patient must still have a good deal of
muscular and nervous plasticity in her arm stump; then, a smart way of
collecting training data must be devised --- an amputee is obviously
not expected to train the machine with a hand. A simple idea is that
of gathering EMG data from the patient's stump and grasping/force data
from her healthy hand, while instructing her to imagine doing the same
actions with both hands. Secondly, the issue of sensorial feedback
will have to be addressed, in order to provide the patient with
reliable information about the force actually involved in the
grasp. This is likely to be crucial in order to realise a tighter and
tighter loop between the patient and the prosthesis.

As far as force regression is concerned, the results presented above
are, to the best of our knowledge, totally novel. Surprisingly,
regression from the forearm surface EMG signal to the force applied by
the hand had never been attempted before. Given the good performance
obtained by our models, we claim that the relationship between the EMG
signal and the force has been captured by the models, under variable
conditions of muscle fatigue (within one session) and electrode
displacement (within sessions belonging to different groups). In a
certain sense, this work is an evolution of the so-called
\emph{proportional} control of myoelectric prostheses already
available on the market; in proportional control, the ``claw'' of the
prosthesis is actuated with a force which is proportional to the
amplitude of the EMG signal. In this case, the applied force is
proportional as well, but the control is realised in a totally natural
way, and is \emph{adaptive} to the user, what has never been done
before.
